PERFILES DE INDIVIDUALISMO Y SU RELACIÓN CON EL APOYO A UN LÍDER FUERTE EN LA SOCIEDAD CHILENA

### 2024-03-26 04-analisis.Rmd
Update 04-analisis.Rmd

datos$clase <- factor(datos$clase, levels = c(1,2,3,4), 
                      labels = c("Individualismo Autoritario",
                                 "Individualismo Conservador",
                                 "Individualismo Liberal",
                                 "Individualismo Agéntico"))

>>>>

datos$clase <- factor(datos$clase, levels = c(1,2,3,4), 
                      labels = c("Individualismo Autoritario",
                                 "Individualismo Conservador",
                                 "Individualismo Liberal",
                                 "Individualismo Estratégico"))
